---
title: "All Responses"
---

```{r load-packages, include=FALSE}
#Load packages that we can assume (for d2m) we all have installed
library(tidyverse)

#TODO: MAKE THESE REQUIRED!
library(bslib)
library(googlesheets4)
library(kableExtra)
library(data.table)
library(lubridate)
library(scales)
library(ggsci)
#library(plotly)
library(thematic)
library(showtext)


```

```{r preferences, echo=FALSE}
# Seed for random number generation
set.seed(6788)
knitr::opts_chunk$set(
    cache.extra = knitr::rand_seed, 
    fig.showtext = TRUE)

# Set theme for plots
theme_set(theme_bw())

#thematic::thematic_rmd(font = "auto")

```

```{r import-raw, include=FALSE}
# 2 OPTIONS FOR DATA READ-IN:

# 1. Read responses from Google sheets
# PRO: Most current data
# CON: Requires appropriate permissions for the google sheet and maintaining settings in the googlesheets4 pkg

gs4_deauth() # Make sure we are not authenticating with any Google account; sheet is publicly viewable
responses_raw <- read_sheet("https://docs.google.com/spreadsheets/d/1T4XEXNxmb3jK2WenIR9vRXggT_-_8HDejP0J3qeXFqM/edit?gid=716006696#gid=716006696")

# 2. Read intermediary dataset 
# current saved file includes responses from Spring 2020 & Winter 2023
# PRO: Data can be publicly accessible and stored in the GitHub repo as a relatively small csv file
# CON: May not include recent response data

#responses_raw <- read_csv("data/responses_raw.csv")

# Note: last 3 columns indicate when the corresponding response is clearly a misinterpretation of the question
# These errors were manually added based purely on human reasoning and healthy skepticism 

```

```{r setup, include = FALSE}

# SOURCE FILES AS NEEDED
source("source/functions.R")
source("source/setup.R")

```


# Managing to meet {.tabset .card .p-3 .mt-6}

## Meeting a stranger

::: {.card .bg-primary}

::: {.card-body}

::: {.card-title}
#### You are meeting a stranger in Chicago.
:::

::: {.card-text}
You both know that you need to meet each other today, but you haven't agreed on a place or a time and you have no means of communication. *Remember, you cannot communicate with them now or previously in any way!*
:::

:::

:::

#### Where do you go to meet a stranger?

```{r str-where, include=FALSE}
# Select stranger meetup column and add cleaning/grouping
# Making it into a data.table allows for easy in-text references (it will be both a df and a dt)

str_meetup <- data.table(clean_meetup(responses, "str_where", "str_error"))

```

::: {.card .m-2}
```{r str-visualize-where, echo=FALSE}

# ?Q?: How many levels display in the legend? Why? Can you change that number in just thisfunction call?
plot_meetup(str_meetup, "str_where_clean")

#ply_str_where <- ggplotly(gg_str_where)

# ?Q?: Since the legend only shows the top n meetup locations (in order), it can be unintuitive what "Other" or "Other (something)" would mean: "Other residence?" Other than what? (other than dorms!). How could you make this more intuitive/understandable?



```
:::

#### When do you meet them?

::: {.card .m-2}
```{r str-visualize-when, echo=FALSE, warning=FALSE}

# Define limits for x-axis time scale
# This visually centers 12pm and makes it show even axis ticks instead of odd (since we want 12 to be clear)
lims <- as.POSIXct(strptime(c("1899-12-29 18:00:00","1899-12-30 18:00:00"), format = "%Y-%m-%d %H:%M:%S")) 

ggplot(filter(responses, !is.na(str_when)), aes(x=str_when)) + 
    geom_histogram(binwidth=360) +
    #geom_density(adjust=1/5) +
    #geom_dotplot() +
    scale_x_datetime(labels = date_format("%H:%M"),
                     date_breaks = "2 hours",
                     limits = lims) +
    theme(axis.text.x = element_text(angle=45)) +
    theme_minimal() +
    labs(x = "TIME OF DAY",
         #title = "Meeting a STRANGER in Chicago, WHEN do you go?",
         subtitle = paste0(nrow(filter(responses,!is.na(str_when))), " total responses"))
    

```
:::

```{css, echo=FALSE}
.scroll-500 {
  max-height: 500px;
  overflow-y: auto;
  background-color: white;
}
```

::: {.card .bg-secondary .p-2}

::: {.card-body}

### Response Breakdown {.tabset} 


#### Times

<span style="color:#f0ad4e">`r round((love_connections/length(str_times))*100,2)`%</span> (`r love_connections` out of `r length(str_times)`) of people chose to meet at **exactly `r format(most_pop_time, "%H:%M")`.**

`r round(((on_the_hour - love_connections)/length(str_times))*100,2)`% chose another time "on the hour" (but not `r format(most_pop_time, "%H:%M")`).

`r round((on_the_thirty/length(str_times))*100,2)`% chose a time "on the half hour."

Just `r round((on_anything_else/length(str_times))*100,2)`% (`r on_anything_else` lonely `r lonely_hearts`) chose anything else.

#### Locations (Grouped)

The most common response for where to meet a *stranger* in Chicago was `r levels(str_meetup$str_where_clean)[1]`, with `r str_meetup[str_where_clean==str_meetup$str_where_clean[1],.N]` responses (`r round((str_meetup[str_where_clean==str_meetup$str_where_clean[1],.N]/str_meetup[,.N])*100,2)`%). <!-- These in-text refs are verbose, but they are entirely data-dependent! If suddenly the Sears tower got way more popular than the Bean, this text would reflect that without any changes. -->

Common responses of Chicago landmarks included the Bean/Cloudgate ($N$ = `r str_meetup[str_where_clean=="The Bean", .N]`), Millennium/Grant Park ($N$ = `r str_meetup[str_where_clean=="Millennium/Grant Park", .N]`), and the Sears/Willis Tower ($N$ = `r str_meetup[str_where_clean=="Sears/Willis Tower", .N]`).

::: {.scroll-500}
```{r str-kable, echo=FALSE, paged.print=TRUE}
# Show kable of all (cleaned) responses with raw counts and percent
kbl_responses(str_meetup, "str_where_clean") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```
:::

#### "Other" Locations 


```{r str-others-response-factors, include=FALSE}
str_others <- Filter(function(x) x %ilike% "Other", levels(str_meetup$str_where_clean))

```

All responses grouped into "Other" categories (`r paste(str_others, collapse=", ")`):

::: {.scroll-500}
```{r str-other-response-list, echo=FALSE}

filter(str_meetup, str_where_clean %in% str_others) %>% 
    mutate(str_where = factor(str_where)) %>% 
    pull(str_where) %>% 
    levels() %>% 
    kable(col.names = c("Other responses")) %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) #%>% 
    #scroll_box(width = "100%", height = "300px")
```
:::

:::
:::

### {-}


## Meeting an unfamiliar student

::: {.card .bg-primary}

::: {.card-body}

::: {.card-title}
#### You are meeting another UChicago student who you have not met before.
:::

::: {.card-text}
You both know that you are both UChicago students and that you should meet today, but you haven't agreed on a meeting location and you have no means of communication. 
:::
:::
:::

#### Where do you go to meet an unknown UChicago student?

```{r student-where, include=FALSE}

student_meetup <- data.table(clean_meetup(responses, "student_where", "student_error"))

```

::: {.card .m-2}
```{r student-visualize-where, echo=FALSE}
plot_meetup(student_meetup, "student_where_clean")
```
:::


::: {.card .bg-secondary .p-2}

::: {.card-body}

### Response Breakdown {.tabset} 

#### Locations (Grouped)

The most common response for where to meet an *unknown UChicago student* in Chicago was `r levels(student_meetup$student_where_clean)[1]`, with `r student_meetup[student_where_clean==student_meetup$student_where_clean[1],.N]` responses (`r round((student_meetup[student_where_clean==student_meetup$student_where_clean[1],.N]/student_meetup[,.N])*100,2)`%). By comparison, `r ifelse(str_meetup[str_where_clean==student_meetup$student_where_clean[1],.N]==0, "no respondents", paste0("only ", str_meetup[str_where_clean==student_meetup$student_where_clean[1],.N], " respondents (", round((str_meetup[str_where_clean==student_meetup$student_where_clean[1],.N]/str_meetup[,.N])*100,2), "%)"))` chose to meet a stranger at `r levels(student_meetup$student_where_clean)[1]`.

While `r levels(str_meetup$str_where_clean)[1]` was the most common response for where to meet a *stranger* in Chicago, `r ifelse(student_meetup[student_where_clean==str_meetup$str_where_clean[1],.N]==0, "no respondents", paste0("only ", student_meetup[student_where_clean==str_meetup$str_where_clean[1],.N], " respondents (", round((student_meetup[student_where_clean==str_meetup$str_where_clean[1],.N]/student_meetup[,.N])*100,2), "%)"))` chose to meet an unfamiliar UChicago student at `r levels(str_meetup$str_where_clean)[1]`.

::: {.scroll-500}
```{r student-kable, echo=FALSE, paged.print=TRUE}
# Show kable of all (cleaned) responses with raw counts and percent
kbl_responses(student_meetup, "student_where_clean") %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```
:::

#### "Other" locations

```{r student-other-response-factors, echo=FALSE}
student_others <- c(Filter(function(x) x %ilike% "Other", levels(student_meetup$student_where_clean)), "Dorms")
```

All responses grouped into "Other" or general categories (`r paste(student_others, collapse=", ")`):

::: {.scroll-500}
```{r student-other-response-list, echo=FALSE}


filter(student_meetup, student_where_clean %in% student_others) %>% 
    mutate(student_where = factor(student_where)) %>% 
    pull(student_where) %>% 
    levels() %>% 
    kable(col.names = c("Other responses")) %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```
:::
:::
:::

### {-}

## Meeting your UChicago friend

::: {.card .bg-primary}

::: {.card-body}

::: {.card-title}
#### You are meeting your closest friend at UChicago.
:::

::: {.card-text}
You haven't agreed on a meeting location and you have no means of communication. 
:::
:::
:::

#### Where do you go to meet your closest UChicago friend?

```{r friend-where, include=FALSE}

friend_meetup <- data.table(clean_meetup(responses, "friend_where", "friend_error"))

```

::: {.card .m-2}
```{r friend-visualize-where, echo=FALSE}

plot_meetup(friend_meetup, "friend_where_clean")

```
:::

::: {.card .bg-secondary .p-2}

::: {.card-body}

### Response Breakdown {.tabset} 

#### Locations (Grouped)

The most common response for where to meet a close UChicago friend in Chicago was `r levels(friend_meetup$friend_where_clean)[1]`, with `r friend_meetup[friend_where_clean==friend_meetup$friend_where_clean[1],.N]` responses (`r round((friend_meetup[friend_where_clean==friend_meetup$friend_where_clean[1],.N]/friend_meetup[,.N])*100,2)`%). By comparison, `r ifelse(str_meetup[str_where_clean==friend_meetup$friend_where_clean[1],.N]==0, "no respondents", paste0("only ", str_meetup[str_where_clean==friend_meetup$friend_where_clean[1],.N], " respondents (", round((str_meetup[str_where_clean==friend_meetup$friend_where_clean[1],.N]/str_meetup[,.N])*100,2), "%)"))` chose to meet a stranger at `r levels(friend_meetup$friend_where_clean)[1]` and `r ifelse(student_meetup[student_where_clean==friend_meetup$friend_where_clean[1],.N]==0, "no respondents", paste0("only ", student_meetup[student_where_clean==friend_meetup$friend_where_clean[1],.N], " respondents (", round((student_meetup[student_where_clean==friend_meetup$friend_where_clean[1],.N]/student_meetup[,.N])*100,2), "%)"))` chose to meet an unknown student at `r levels(friend_meetup$friend_where_clean)[1]`.

While `r levels(str_meetup$str_where_clean)[1]` was the most common response for where to meet a *stranger* in Chicago, `r ifelse(friend_meetup[friend_where_clean==str_meetup$str_where_clean[1],.N]==0, "no respondents", paste0("only ", friend_meetup[friend_where_clean==str_meetup$str_where_clean[1],.N], " respondents (", round((friend_meetup[friend_where_clean==str_meetup$str_where_clean[1],.N]/friend_meetup[,.N])*100,2), "%)"))` chose to meet a close UChicago friend at `r levels(str_meetup$str_where_clean)[1]`.

`r levels(student_meetup$student_where_clean)[1]` was the most common response for where to meet an *unfamiliar UChicago student* in Chicago, but `r ifelse(friend_meetup[friend_where_clean==student_meetup$student_where_clean[1],.N]==0, "no respondents", paste0("only ", friend_meetup[friend_where_clean==student_meetup$student_where_clean[1],.N], " respondents (", round((friend_meetup[friend_where_clean==student_meetup$student_where_clean[1],.N]/friend_meetup[,.N])*100,2), "%)"))` chose to meet a close UChicago friend at `r levels(student_meetup$student_where_clean)[1]`.

::: {.scroll-500}
```{r friend-kable, echo=FALSE, paged.print=TRUE}
# Show kable of all (cleaned) responses with raw counts and percent
kbl_responses(friend_meetup, "friend_where_clean") %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```
:::

#### "Other" Locations


```{r friend-other-response-factors, echo=FALSE}

friend_others <- c(Filter(function(x) x %ilike% "Other", levels(friend_meetup$friend_where_clean)), "Dorms", "Recent meeting location")

```


All responses grouped into "Other" or general categories (`r paste(friend_others, collapse=", ")`):

::: {.scroll-500}
```{r friend-other-response-list, echo=FALSE, message=FALSE, warning=FALSE}

filter(friend_meetup, friend_where_clean %in% friend_others) %>% 
    mutate(friend_where = factor(friend_where)) %>% 
    pull(friend_where) %>% 
    levels() %>% 
    kable(col.names = c("Other responses")) %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```
:::

:::
:::

### {-}

## {-}

# Coin Flip {.tabset .card .p-3}

You and an anonymous partner need to choose heads or tails.

```{r anon-responses, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
responses_anon <- responses %>% 
    select(coin_same, coin_different, number_0to10, number_selection, number_big) %>% 
    drop_na()
    
```

```{r coins, echo=FALSE, message=FALSE, warning=FALSE}
coins <- select(responses_anon, coin_same, coin_different) %>% 
    pivot_longer(cols = c(coin_same, coin_different), names_to = "goal", names_prefix = "coin_", values_to = "side")

coins$goal <- fct_recode(coins$goal, 'Choose same' = "same", 'Choose different' = "different")
    

```


## Same

::: {.card .bg-primary}

::: {.card-body}

::: {.card-title}
#### Aim to match.
:::

::: {.card-text}
If you both choose the **SAME** answer, you both win. Which do you choose?
:::

:::

:::

::: {.card .m-2 .p-2}
```{r coins-visualize-same, echo=FALSE, message=FALSE, warning=FALSE}
filter(coins, goal=="Choose same") %>% 
ggplot(aes(x="", fill = side)) + 
    geom_bar(width=.8) +  
    coord_polar("y", start=0) +
    geom_label(stat="count", aes(label=stat(count), group=side), 
               position = position_stack(vjust = .5),
               show.legend = F,
               fill="white") +
    theme_void() +
    #facet_wrap(vars(fct_rev(goal))) +
    theme(strip.text = element_text(size = 20)) +
    labs(fill = "Coin side") +
    scale_fill_manual(values=pal_futurama()(10)[5:7])
```
:::

## Different

::: {.card .bg-primary}

::: {.card-body}

::: {.card-title}
#### Aim to differ.
:::

::: {.card-text}
If you both choose the **DIFFERENT** answers, you both win. Which do you choose?
:::

:::

:::

::: {.card .m-2 .p-2}
```{r coins-visualize-diff, echo=FALSE, message=FALSE, warning=FALSE}
filter(coins, goal=="Choose different") %>% 
ggplot(aes(x="", fill = side)) + 
    geom_bar(width=.8) +  
    coord_polar("y", start=0) +
    geom_label(stat="count", aes(label=stat(count), group=side), 
               position = position_stack(vjust = .5),
               show.legend = F,
               fill="white") +
    theme_void() +
    #facet_wrap(vars(fct_rev(goal))) +
    theme(strip.text = element_text(size = 20)) +
    labs(fill = "Coin side") +
    scale_fill_manual(values=pal_futurama()(10)[5:7])
```
:::

## Table

::: {.card .bg-secondary}

::: {.card-body}

::: {.card-title}
#### Percent choice
:::

::: {.mb-2 style="background-color: white;"}
```{r coins-props, echo=FALSE}
round(addmargins(proportions(table(fct_rev(coins$goal), coins$side),1)*100,2),2) %>% kable() %>%  kable_styling(bootstrap_options = c("striped", "hover", "responsive"))
```
:::

:::

:::






# Numbers {.tabset .card .p-3}

```{r numbers, include=FALSE}
numbers <- responses_anon %>% 
    select(starts_with("number")) %>% 
    mutate(across(1:2, factor, ordered=T),
           number_big_fct = factor(number_big, ordered=T)) %>% 
    na.omit()

```

## 0 to 10

::: {.card .bg-primary}

::: {.card-body}

::: {.card-title}
### Pick a number 0 to 10.
:::

::: {.card-text}
You win if you match your partner.
:::

:::

:::

::: {.card .m-2}
```{r number-0to10-visualize, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(numbers, aes(x=number_0to10, fill=number_0to10)) + 
    geom_bar() +
    #theme_minimal() +
    labs(#title="Match an anonymous partner: select 0-10",
         y=element_blank(),
         x=element_blank()) +
    theme(axis.text.x = element_text(size=24),
          legend.position = "none") +
    scale_fill_futurama()

```
:::

## Fixed set

::: {.card .bg-primary}

::: {.card-body}

::: {.card-title}
### Select a number from the set.
:::

::: {.card-text}
You win if you match your partner.
:::

:::
:::

::: {.card .m-2}
```{r number-selection-visualize, echo=FALSE, message=TRUE, warning=TRUE}

ggplot(numbers, aes(x=number_selection, fill=number_selection)) + 
    geom_bar() +
    theme_minimal() +
    labs(#title="Match an anonymous partner: select among these numbers",
         y=element_blank(),
         x=element_blank()) +
    theme(axis.text.x = element_text(size=20),
          legend.position = "none") +
    scale_fill_futurama()
```
:::


## Bigger the better

::: {.card .bg-primary}

::: {.card-body}

::: {.card-title}
### Pick any number.
:::

::: {.card-text}
You win if you match your partner, *and* the bigger the number, the more you both win.
:::

:::
:::

::: {.card .m-2}
```{r number-big-visualize, echo=FALSE, message=FALSE, warning=FALSE}

mutate(numbers, number_big = factor(as.integer(number_big))) %>% 
    filter(!is.na(number_big)) %>% 
ggplot(aes(x=number_big)) + 
    geom_bar(aes(fill=factor(as.integer(number_big)))) +
    #geom_histogram(binwidth = 10) +
    theme_minimal() +
    labs(#title="Match an anonymous partner: the bigger the better",
         y=element_blank(),
         x=element_blank()) +
    theme(axis.text.x = element_text(size=10, angle=90, hjust=1),
          legend.position = "none") 
```
:::
